<<<<<<< HEAD
---
title: "The Role of Governments in Attracting GVC Operations"
author: "Rami Osman, Jingjing Luo, Hossein Farahi"
date: "09/02/2022"
output: 
  html_document: 
    toc: yes
    toc_depth: 3
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Talk about what the project is and why it is important (context). Make sure to include references at every stage in the project. Example sub-sectinos below:

## Define GVCs

## Emergence of GVCs
Talk about globalization...etc

## Types of GVCs

## Role of GVCs
Connecting the world

### Advantages

### Disadvantages

## Structure of GVCs

## Where do governments fit in

## Why is GVC participation important for developing countries?
Reduce unemployment, cross fertilizations leading to reverse innovation, decrease financial burdens on debeloped countries, streamline global economic recovery. Use this section as a segway to introduce the research question, what the dependent variable is and the corresponding independent variables that will help us test the dependent variable correlations. Mention the limitations, differences between developing to developing country VS developing to developed country VS Developed to developed country considerations to attract GVCs

**MENTION RESEARCH QUESTION IN BOLD ON A LINE ON ITS OWN**

# Literature Review

# Exploratory Data Analysis
Use the independent variables we selected to build our model here and analyse our results. We're most probably going to use panel data to show what action governments take that work and what actions they take that make no difference. Run correlations, plm, ggplots, stargazer...etc

# Models

# Results and Implications (policies, strategies...etc)


# Conclusion

# References
Use Zotero

=======
---
title: "The Role of Governments in Attracting GVC Operations"
author: "Rami Osman, Jingjing Lu, Hossein Farahi"
date: "09/02/2022"
output: 
  html_document: 
    toc: yes
    toc_depth: 3
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Talk about what the project is and why it is important (context). Make sure to include references at every stage in the project. Example sub-sectinos below:

## Define GVCs

## Role of GVCs
Connecting the world

### Advantages

### Disadvantages

## Structure of GVCs

## Where do governments fit in

## Why is GVC participation important for developing countries?
Reduce unemployment, cross fertilizations leading to reverse innovation, decrease financial burdens on debeloped countries, streamline global economic recovery. Use this section as a segway to introduce the research question, what the dependent variable is and the corresponding independent variables that will help us test the dependent variable correlations. Mention the limitations, differences between developing to developing country VS developing to developed country VS Developed to developed country considerations to attract GVCs

**MENTION RESEARCH QUESTION IN BOLD ON A LINE ON ITS OWN**

# Literature Review
the effect of the legislation on the GVC
Why FDI can represent the performance of GVC
why GCI and SPI can represent the effect of CPI

# Exploratory Data Analysis
Use the independent variables we selected to build our model here and analyse our results. We're most probably going to use panel data to show what action governments take that work and what actions they take that make no difference. Run correlations, plm, ggplots, stargazer...etc

# Models

# Results and Implications (policies, strategies...etc)
•	How will legislation affect GVC performance?
•	What types of countries need to be involved more in terms of legislation in the GVC activities?
•	What's the difference between the contribution of the manufacturing and service industry between developing countries and developing countries? In more detail, in developing countries, does manufacturing or service contribute more to the performance of GVC in total?

# Conclusion

# References
Use Zotero

>>>>>>> 3a1267705b4e84bdc78816b58a8497d880b0fb74
